MSD panels 1, 2 and 3 Explant Sup

### 2016-08-23 MSD_panels_1_2_3_explant_sup_analysis.Rmd
Multiplied the concentrations of the sup by 5 to estimate stock concentration

ggplot(explant_all_panels_noStds_Below, aes(x = Assay, y=Number_of_Samples))+
         geom_point(aes(color = Detection.Range),size = 2)+
  theme(axis.text.x = element_text(angle=25, size = 8))+
  labs(y = "Number of Samples", x = "Analyte")+
  facet_wrap(~Panel, scales = "free")+
  ggtitle("Number of Samples in each Detection Range per Analyte")

@@

Black points show the means.

@@

@@

     ggplot( aes(x = Timepoint, y = avgConc))+

@@

   labs( y = "Concentration")+

@@

   theme(axis.text.x = element_text(angle = 25, size = 9))+
     ggtitle(Analyte)
}

>>>>

ggplot(explant_all_panels_noStds_Below, aes(x = Assay, y=Number_of_Samples))+
         geom_point(aes(color = Detection.Range),size = 2)+
  theme(axis.text.x = element_text(angle=25, size = 7))+
  labs(y = "Number of Samples", x = "Analyte")+
  facet_wrap(~Panel, scales = "free")+
  ggtitle("Number of Samples in each Detection Range per Analyte")

@@

We did a 1:5 dilution of the samples so I multiplied the concentrations by 5 to get an estimate of the stock suparnatent concentration. Black points show the means.

@@

#I'm going to make a column for estimated stock concentration by multiplying the avgConc by 5 (since I did a 1:5 dilution on the samples) so I can better compare with the HVE sup concentrations.

avgConc_explant_all_panels_noStds_noBelow_fullSet <- avgConc_explant_all_panels_noStds_noBelow_fullSet %>%
  mutate (Estimated_Stock_Conc = avgConc * 5)

@@

     ggplot( aes(x = Timepoint, y = Estimated_Stock_Conc))+

@@

   labs( y = "Concentration pg/ml")+

@@

   theme(axis.text.x = element_text(size = 11))+
     ggtitle(Analyte)
}
